First Class Pattern Matching in a Deeply Embedded Domain Specific Language\\ \large{Not For Distribution}

### 2020-04-21 paper/paper.tex
Some advice for readers
Formatting

@@

The \ttt{Name t} type represents a lambda variable identifier together with its
type \ttt{t} (Note that the \ttt{ScopedTypeVariables} extension is enabled.):

>>>>

Readers who are primarily interested only in the encoding of pattern matching itself can direct
most of their attention to sections 2, 3 and 6.

@@

The \ttt{Name t} type represents a lambda variable identifier together with its
type \ttt{t} (Note that the \ttt{ScopedTypeVariables} extension is enabled):
